An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex

To solve this problem, peers in our system periodically check on the nodes that they are using as backup locations in order to gauge how available they are. During normal program operation, each peer tests the availability of its replication nodes via a challenge mechanism, described in section \ref{subsec:ChallengeMechanism_sec:Fairness}. The challenge mechanism not only ensures the node is online, but also confirms it is storing the peer's data. If the replication node is online and passes the challenge, the peer does not need to do anything; it will continue to (accurately) think that the node is reliable. If the node fails the challenge (by being offline or not storing the user's data), however, the peer will take note that the node was unreliable in this instance. It would be unfair to immediately conclude that the node is consistently unreliable, since it may have been temporarily offline (for example, a user temporarily shutting down his/her computer). Therefore, a node needs to fail the challenge mechanism several times before the peer concludes that it is consistently unreliable. It is possible that a node gets unlucky and happens to be offline during all checks, even though it is online during a different part of the day. If this is the case, then the node is not frequently available for that peer, and should be seen as consistently unreliable from the peer's perspective.

When a peer determines that a node is consistently unreliable, it does two things. The first is that it adds its own ID to the node's blacklist in the DHT. The second is to move its replica to a new node. The peer sends an update to the DHT that it is removing the replica on the unreliable node. This accomplishes two things: all other peers in the network can see that the node is storing less data, and the node can see that it no longer needs to store the replica, so it can remove it the next time it checks the DHT for any changes. The peer will then look for a new node to put a replica on, using the same process that was used for creating the original backups (see section \ref{sec:TheMetadataLayer}). Since this process uses a randomly generated salt to help pick the ID of the new node, each node has an equal chance of being selected, assuming that it has enough space to store the replica and is not blacklisted by too many peers. This helps to prevent some nodes from being left out of the selection process. % TODO this last sentence can be removed without loss of information

>>>>

To solve this problem, peers in our system periodically check on the nodes that they are using as backup locations in order to gauge how available they are. During normal program operation, each peer tests the availability of its replication nodes via a challenge mechanism, described in section \ref{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}. The challenge mechanism not only ensures the node is online, but also confirms it is storing the peer's data. If the replication node is online and passes the challenge, the peer does not need to do anything; it will continue to (accurately) think that the node is reliable. If the node fails the challenge (by being offline or not storing the user's data), however, the peer will take note that the node was unreliable in this instance. It would be unfair to immediately conclude that the node is consistently unreliable, since it may have been temporarily offline (for example, a user temporarily shutting down his/her computer). Therefore, a node needs to fail the challenge mechanism several times before the peer concludes that it is consistently unreliable. It is possible that a node gets unlucky and happens to be offline during all checks, even though it is online during a different part of the day. If this is the case, then the node is not frequently available for that peer, and should be seen as consistently unreliable from the peer's perspective.

When a peer determines that a node is consistently unreliable, it does two things. The first is that it adds its own ID to the node's blacklist in the DHT. The second is to move its replica to a new node. The peer sends an update to the DHT that it is removing the replica on the unreliable node. This accomplishes two things: all other peers in the network can see that the node is storing less data, and the node can see that it no longer needs to store the replica, so it can remove it the next time it checks the DHT for any changes. The peer will then look for a new node to put a replica on, using the same process that was used for creating the original backups (see section \ref{subsec:TheMetadataLayer_sec:SystemDesign}). Since this process uses a randomly generated salt to help pick the ID of the new node, each node has an equal chance of being selected, assuming that it has enough space to store the replica and is not blacklisted by too many peers. This helps to prevent some nodes from being left out of the selection process. % TODO this last sentence can be removed without loss of information, but it might mean that the salt explanation in the crypto section was for nothing.
